Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-06-03 ms.tex
made a comparison with BOSZ models and Kento's spectrum.
added a little about the BOSZ models and references to Seager 2003 for the stellar density measurement.

The host star \shStar\ has been characterized by both photometry and spectroscopy.
Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}
\citet{vanlieshout2016kic1255} analyze the light curve with a dust model and find a constraint on the semi-major axis which, in term, constraints the density of the star.
\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
If true, this would suggest that high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.

@@

The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
Figure \ref{fig:prof2013vs2015} shows an example blue-chip image from 2013 and 2015.
The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm) has a sharper PSF and and is easier to trace.
The 2013 data was taken with an image slicer and a wider ((2 $\times$ 30 mm)) slit, which create 3 parallel traces for \shStar.
A flat field with a narrower (0.3 mm) slit is needed to create a trace for use with the image slicer.
For wavelength identification, a Thorium Argon reference is used.
(Not to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
The final rms in this wavelength solution is 0.0021 $\AA$.
After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines} and the

@@

>>>>

The host star \shStar\ has been characterized by both photometry and spectroscopy.
Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis, which in turn constrains the density of the star when combined with Kepler's third law \citep{seager2003uniqueSolution}.
\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
If true, this would suggest that high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.

@@

The 2013 HDS data and 2015 HDS data were taken in slightly different modes.
Figure \ref{fig:prof2013vs2015} shows an example blue-chip image from 2013 and 2015.
The 2015 data, with a narrow slit (0.3 $\times$ 3.5 mm) has a sharper PSF and and is easier to trace.
The 2013 data was taken with a wider (2 $\times$ 30 mm) slit and an image slicer, which create 3 parallel traces for \shStar.
A flat field with a narrower (0.3 mm) slit is needed to create a trace for use with the image slicer.
For wavelength identification, a Thorium Argon reference is used.
(Not to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas.
The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
The final rms in this wavelength solution is 0.0021 $\AA$.
After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines} and the

@@

\subsection{Comparison to BOSZ}

The BOSZ models \citep{bohlin2017bosz} are calculated up to a resolution of 300,000, so we use these to compare to the measured spectra.
We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTriplet}.

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet.pdf}
\caption{Example spectrum of \shStar\ (reduced by Kento Mashuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTriplet}
\end{centering}
\end{figure}
